\section{Important information}
\subsection{Trademarks and affiliation}
"PlayStation", "PlayStation Family Mark", "PS5 logo", "PS5", "DualSense" and "DUALSHOCK" are registered trademarks or trademarks of Sony Interactive Entertainment Inc. "SONY" is a registered trademark of Sony Corporation.

\textbf{The Author is not affiliated in any kind with Sony Interactive Entertainment Inc.!} \\
Using this library may void your / your clients / your users / your customers controllers warranty! You as the redistributor of the precompiled or self compiled library have to make sure the controller will not be damaged by the functionality you use or at least point out the possible risk to your users / clients / customer!\\
Probably no damage or failure at all. This statement is just for my own safety!

\subsection{Sources}
This work is derivative from others work. Special thanks goes to:
\begin{itemize}
	\item GitHub user dogtopus: \\ \url{https://gist.github.com/dogtopus/894da226d73afb3bdd195df41b3a26aa}.
	\item Reddit user ginkgobitter: \url{https://www.reddit.com/r/gamedev/comments/jumvi5/dualsense_haptics_leds_and_more_hid_output_report/}
	\item GitHub user Ryochan7: \url{https://github.com/Ryochan7/DS4Windows/tree/dualsense-integration} \\ Copyright (c) 2019 Travis Nickles - MIT License: \url{https://github.com/Ryochan7/DS4Windows/blob/jay/LICENSE.txt} 
	\item And the amazing community at DS4Windows \url{https://github.com/Ryochan7/DS4Windows/issues/1545}
	
\end{itemize}
\newpage

\subsection{License}
\textbf{MIT License}\\

Copyright (c) 2020 Ludwig Füchsl\\

Permission is hereby granted, free of charge, to any person obtaining a copy of this software and associated documentation files (the "Software"), to deal in the Software without restriction, including without limitation the rights to use, copy, modify, merge, publish, distribute, sublicense, and/or sell copies of the Software, and to permit persons to whom the Software is furnished to do so, subject to the following conditions:\\

The above copyright notice and this permission notice shall be included in all copies or substantial portions of the Software.\\

THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE SOFTWARE.

\newpage